### 2020-12-18 paper/sex_selection_spacing-ver5.tex
Key independent variables in Introduction
- Also, one more birth interval length problem

The primary outcomes I examine are the 25th, 50th, and 75th percentile birth intervals;
the sex ratio at birth; and the likelihood of giving birth. 
I estimate the model across four periods to capture the changing access and 
legality of sex selection. 
The key variables are maternal education, the sex of previous children, and the area of 
residence.

>>>>

The primary outcomes I examine are the 25th, 50th, and 75th percentile birth intervals lengths;
the sex ratio at birth; and the likelihood of giving birth. 
I estimate the model across four periods to capture the changing access and 
legality of sex selection. 
The key independent variables are maternal education, the sex of previous children, and 
the area of residence.
